Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-01-25 paper.tex
Add paragraph about compressive sensing.

Indeed, the bound in Theorem~\ref{thm:main-lb} assumes that an arbitrarily
large number of sensors can be squeezed into a finite amount of space, and that
these sensors \emph{still} have the same SNR.  This is aphysical, since in
reality, each sensor has a certain width, and the value measured by it is the
integral of the continuous-space signal within that width (analogous to a
sample-and-hold circuit, which integrates a continuous-\emph{time} signal over
a short period).  If the width of a sensor is decreased, then effectively, its
SNR reduces.  This is intuitively evident in the sample-and-hold analogy: to
compute the signal value, the integral must be divided by the time interval
over which the integration is performed; this division amplifies noise as the
time interval gets smaller.

@@

%This bound is valid for any pair of hypotheses $\theta_0$ and $\theta_1$,
%separated by a distance of $2\delta$.
%As $\delta$ increases, it becomes
%easier to distinguish between the two hypotheses, so $P_e$ falls. When
%numerically evaluating the bound, therefore, we have to \emph{manually}
%trade-off between $\delta$ and $P_e$ to find the tightest possible bound. This
%comes down to choosing $\theta_0$ and $\theta_1$ so that they are the hardest
%hypotheses to distinguish between. To make the simulation easier, we can relax
%the process of finding the least discernable hypothesis pair by fixing
%$\theta_0$. Then, we need only optimize over $\delta$, making the process more
%tractable. This comes at the cost of loosening the lower bound.

@@

@@

While the bounds in section~\ref{sec:lecam-lb} were derived for a
one-dimensional circular domain, extensions to a one-dimensional linear domain
(of fixed length) and to a $d$-dimensional domain (circular or linear) are
fairly straightforward, under certain conditions. For a 1D linear domain, we
require that sensors capture the entirety of the impulse response even at the
edges of the domain. Hence, sensors must be placed uniformly in $[-w/2,
S{+}w/2]$. For extending to $d$ dimensions, it suffices to apply Assouad's
Lemma~\cite{Tsybakov2009Introduction} to separate the problem into $d$
independent one-dimensional problems.

>>>>

Indeed, the bound in Theorem~\ref{thm:main-lb} assumes that an arbitrarily
large number of sensors can be squeezed into a finite amount of space, and that
these sensors \emph{still} have the same SNR.  This is non-physical, since in
reality, each sensor has a certain width, and the value measured by it is the
integral of the continuous-space signal within that width (analogous to a
sample-and-hold circuit, which integrates a continuous-\emph{time} signal over
a short period).  If the width of a sensor is decreased, then effectively, its
SNR reduces.  This is intuitively evident in the sample-and-hold analogy: to
compute the signal value, the integral must be divided by the time interval
over which the integration is performed; this division amplifies noise as the
time interval gets smaller.

@@

@@

We also note that the minimax bounds from compressive sensing
literature~\cite{AriasCastro2013Fundamental} do not apply in our setting,
because those consider the problem of recovering the whole source signal,
$x(s;\theta)$. The loss function used there is hence the energy of the
difference signal $\int \abs{x(s) - \hat x(s)}^2 ds$. We, on the other hand,
are interested in bounding the minimax error in \emph{location}, i.e.,
$\abs{\theta - \hat\theta}^2$.

While the bounds in section~\ref{sec:lecam-lb} were derived for a
one-dimensional circular domain, extensions to a one-dimensional linear domain
(of fixed length) and to a $d$-dimensional domain (circular or linear) are
fairly straightforward, under certain conditions. For a 1D linear domain, we
require that sensors capture the entirety of the impulse response even at the
edges of the domain. Hence, sensors must be placed uniformly in $[-w/2,
S{+}w/2]$. For extending to $d$ dimensions, it suffices to apply Assouad's
Lemma~\cite{Tsybakov2009Introduction} to separate the problem into $d$
independent one-dimensional problems. Such extensions substantially broaden the
number of settings in which this bound applies.

@@
